---
title: "Untitled"
author: "JonathanYde"
date: "17. jun. 2015"
output: slidy_presentation
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with code

This is a GoogleVis plot:

```{r libraries, echo=FALSE, message=FALSE}
library(ggplot2)
library(googleVis)
library(datasets)
suppressPackageStartupMessages(library(googleVis))
op <- options(gvis.plot.tag="chart")
```

```{r}
data(mpg)
head(mpg)
```

## Slide with code
```{r Bubbledata}
chart <- gvisBubbleChart(mpg, idvar="manufacturer",
  xvar="cty",
  yvar="hwy",
  colorvar="year",
  sizevar="class",
  options=list(
                            hAxis="{title:'Cty'}",
                            vAxis="{title:'Hwy'}",
                            width=900,
                            height=600
  )
)
```

## Slide with graph
```{r plotBubble, results='asis', echo=FALSE, message=FALSE}
print(chart, "chart")
```